---
title: "Capstone - Sampling the data"
author: "Kristian Gårdhus Wichmann"
date: "10 feb 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Handling large datasets - sampling
The three data files are huge. Holding all of them in active memory at the same time will be different for most computers. To handle this, a random sample of 5% is chosen from each.

### Blogs

Load the blogs data:
```{r}
blogs <- readLines("en_US/en_US.blogs.txt")
```

Take sample:
```{r}
samplesize <- floor(length(blogs) * 0.05)
blogs_sample <- sample(blogs, samplesize)
```

To free memory, delete the blogs:
```{r}
rm(blogs)
```

### News

Load the blogs data:
```{r}
news <- readLines("en_US/en_US.news.txt")
```

The warning simply means that the file has no line break at the end. Take sample:
```{r}
samplesize <- floor(length(news) * 0.05)
news_sample <- sample(news, samplesize)
```

Delete news:
```{r}
rm(news)
```
### Tweets

Load the tweets data:
```{r}
tweets <- readLines("en_US/en_US.twitter.txt")
```

Inspect the lines mentioned in warnings:
```{r}
tweets[c(167155, 268547, 1274086, 1759032)]
```

There's nothing appearantly suspicious about these. Now a sample is chosen:
```{r}
set.seed(42)
samplesize <- floor(length(tweets) * 0.05)
tweets_sample <- sample(tweets, samplesize)
```

Delete tweets:
```{r}
rm(tweets)
```

## Save the data
Finally, the three data sets are saved:
```{r}
write(blogs_sample, "blogs_sample")
write(news_sample, "news_sample")
write(tweets_sample, "tweets_sample")
```